Paper 1

### 2018-09-15 paper1.tex
Finalized the paper 1

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% THE ABOVE CLAIMED PROOF IS INCORRECT.
% WRITE A FEW SENTENCES TO EXPLAIN THE ERROR.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
Although the theorem is true, the proof is not adequate.
The negation on the theorem's statement is done incorrectly. 
The statement is, $\forall a,b,c >0$, 
$$
	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} \geq 3.
$$ 
The correct negation would then be: there $\exists a,b,c >0$ such that 
$$
	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} < 3.
$$
The proof by contradiction above is done by giving one counterexample against the negation.
However, this is not sufficient because you have to show that do not exist $a,b,$ or $c >0$ that satisfies the property. 
Therefore, the proof is incorrect.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
	%%%%%%%%%%22%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Use the AM-GM inequality.
	%
	\begin{comment} %My initial longer solution
		From the AM-GM inequality, we know
		\begin{align*}
		\frac{a+b+c}{3} \geq \sqrt[3]{abc}. 
		\end{align*}
		Because we know $abc$ is a positive number, $\sqrt[3]{abc}$ is also positive. So, we can perform the following,
		\begin{align*}
		\frac{(a+b+c)(\sqrt[3]{abc})^2}{3} &\geq abc \\
		\frac{(a+b+c)}{(abc)^{\frac{1}{3}}} &\geq 3 \\
		\frac{(a)^{\frac{2}{3}}}{(bc)^{\frac{1}{3}}} + \frac{(b)^{\frac{2}{3}}}{(ac)^{\frac{1}{3}}} + \frac{(c)^{\frac{2}{3}}}{(ab)^{\frac{1}{3}}}&\geq 3 \\
		\sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}&\geq 3
		\end{align*}
		We know that all terms are positive in the above inequality, so,
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq \sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}\geq3.$$
		This implies that 
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq 3 .$$
	\end{comment}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

So, the proof does not prove the theorem, but it was able to prove, through induction, that $x=a^m/b$ works and $x=a/b^n$ works independently. 
However, it does not follow that for every $m,n\in\NN$, and for every positive $x\in\QQ$, there exist $a,b\in\NN$ such that $x = a^m / b^n$.

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% First you have to complete the statement of the lemma.
	% This means that you have to replace both $\phi(a_n,b_n)$ and $\psi(a_n,b_n)$ with explicit formulae.
	% There is no need to show how you worked out what should replace $\phi$ and $\psi$, just enter the replacements into the statement of the lemma and then give the proof as if you always had always known what $\phi$ and $\psi$ are.
	% THE SYMBOLS $\phi$ AND $\psi$ SHOULD NOT APPEAR ANYWHERE IN THE STATEMENT OF THE LEMMA OR THE PROOF WHEN YOU SUBMIT.
	%
	% The proof is by induction.
	%
	First, we want to show that the sequence satisfies the first equation,
	$$\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2}.$$
	When $n=1$ the equations holds,
	\begin{align*}
		\mbox{LHS} = \left(1+\sqrt{2}\right)^1=1+\sqrt{2}\\	
		\mbox{RHS} = a_1+b_1\sqrt{2}=1+\sqrt{2}.
	\end{align*}
	So, $\mbox{LHS} = \mbox{RHS},$ and the equation holds for $n=1$.
	Assume the equations holds for a particular natural number $n$.
	Now, we want to show that the equation also holds for $n+1$.
	From our assumption we know,
	\begin{align*}
		\left(1+\sqrt{2}\right)^n &= a_n + b_n \sqrt{2}\\
		\left(1+\sqrt{2}\right)^n(1+\sqrt{2}) &= (a_n + b_n \sqrt{2})(1+\sqrt{2})\\
		\left(1+\sqrt{2}\right)^{n+1}&= a_n + a_n\sqrt{2} + b_n\sqrt{2} +2b_n\\
		\left(1+\sqrt{2}\right)^{n+1}&= (a_n+2b_n) + (a_n+b_n)\sqrt{2}\\
		\left(1+\sqrt{2}\right)^{n+1} &= (a_{n+1}) + (b_{n+1})\sqrt{2}
	\end{align*}
	Hence, the equation holds for $n+1$ when it holds for $n$. 
	By induction on $n$, the equation holds for all natural number $n$.

@@

	If $x+1$ is divisible by $n$, then $\frac{x+1}{n}\in \NNzero$ and $0\leq\frac{x+1}{n}\leq x$. Since we know that $P(k)$ is true, we know that there exists an $n$-ary sequence such that 
	$$
		\frac{x+1}{n} = \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^j
	$$
	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $(a_{\frac{x+1}{n}})_{j\in\NN^0}$
	Manipulating this equation yields, 
	\begin{align*}
		x+1 &= \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^{j+1} \\
		x+1 &= \sum_{j=1}^\infty a_{\frac{x+1}{n},j-1} n^{j}.
	\end{align*}
	Now, let us define a new sequence $(a_{x+1,j})_{j\in\NN^0}$ such that $a_{x+1,j} = a_{\frac{x+1}{n},j-1}$ for all $j\in \NN$ and $a_{x+1,0} = 0 $. We can then rewrite the previous equation as
	\begin{align*}
		x+1 &= 0+ \sum_{j=1}^\infty a_{x+1,j} n^{j} \\
		x+1 &=  \sum_{j=0}^\infty a_{x+1,j} n^{j}.
	\end{align*}
	This new sequence is eventually zero because the original sequence $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ was eventually zero. 
	This new sequence is also $n$-ary because $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ is $n$-ary and we only added another $0$. So we have shown that $P(x+1)$ is true if $x+1$ is divisible by $n$.

	Next, consider the case where $x+1$ is not divisible by $n$. 
	Then, the quotient remainder theorem states that there exists an integer $r$, $1\leq r\leq n-1$ such that $\frac{x+1-r}{n} \in \NN$. 
	So, we can write $0\leq\frac{x+1-r}{n}\leq x$. By our inductive hypothesis, we know
	\begin{align*}
		\frac{x+1-r}{n} &= \sum_{j=0}^\infty a_{\frac{x+1-r}{n},j} n^{j} \\
		x+1-r &= \sum_{j=0}^\infty a_{\frac{x+1-r}{n},j} n^{j+1} \\
		x+1 &= r + \sum_{j=1}^\infty a_{\frac{x+1-r}{n},j-1} n^{j}.
	\end{align*}
	Now, we can define a new sequence $(a_{x+1,j})_{j\in\NN^0}$ such that $a_{x+1,j} = a_{\frac{x+1-r}{n},j-1}$ for all $j\in \NN$ and $a_{x+1,0} = r $. We can then rewrite the previous equation as
	\begin{align*}
		x+1 &= r + \sum_{j=1}^\infty a_{x+1,j} n^{j}\\
		x+1 &= \sum_{j=0}^\infty a_{x+1,j} n^{j}.
	\end{align*}
	This new sequence is eventually zero because the original sequence  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ was eventually zero. This new sequence is also $n$-ary because  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ is $n$-ary, and we added an additional term $r$ which is $1\leq r\leq n-1$. So we have shown that $P(x+1)$ is also true if $x+1$ is not divisible by $n$.

	Therefore $P(x+1)$ is true for all $n\geq2$. By complete induction on $x$, $P(x)$ is true, and the theorem is proved.

>>>>

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% THE ABOVE CLAIMED PROOF IS INCORRECT.
% WRITE A FEW SENTENCES TO EXPLAIN THE ERROR.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
Although the theorem is true, the proof is not adequate.
The negation on the theorem's statement is done incorrectly. 
The statement is, $\forall a,b,c >0$, 
$$
	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} \geq 3.
$$ 
The correct negation would then be: there $\exists a,b,c >0$ such that 
$$
	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} < 3.
$$
The proof by contradiction above is done by giving one counterexample against the negation.
However, this is not sufficient because you have to show that do not exist $a,b,$ or $c >0$ that satisfies the property. 
Therefore, the proof is incorrect. However, it was very efficient by showing a simple counterexample, albeit not enough to prove the theorem.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Use the AM-GM inequality.
	%
	\begin{comment} %My initial longer solution
		From the AM-GM inequality, we know
		\begin{align*}
		\frac{a+b+c}{3} \geq \sqrt[3]{abc}. 
		\end{align*}
		Because we know $abc$ is a positive number, $\sqrt[3]{abc}$ is also positive. So, we can perform the following,
		\begin{align*}
		\frac{(a+b+c)(\sqrt[3]{abc})^2}{3} &\geq abc \\
		\frac{(a+b+c)}{(abc)^{\frac{1}{3}}} &\geq 3 \\
		\frac{(a)^{\frac{2}{3}}}{(bc)^{\frac{1}{3}}} + \frac{(b)^{\frac{2}{3}}}{(ac)^{\frac{1}{3}}} + \frac{(c)^{\frac{2}{3}}}{(ab)^{\frac{1}{3}}}&\geq 3 \\
		\sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}&\geq 3
		\end{align*}
		We know that all terms are positive in the above inequality, so,
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq \sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}\geq3.$$
		This implies that 
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq 3 .$$
	\end{comment}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

So, the proof does not prove the theorem, but it was able to prove, through induction, that $x=a^m/b$ works and $x=a/b^n$ works independently. 
The proof was very efficient in the induction portion by showing very clearly what the base case, the hypothesis, and the inductive step are without doing so too repetitively.
However, it does not follow that for every $m,n\in\NN$, and for every positive $x\in\QQ$, there exist $a,b\in\NN$ such that $x = a^m / b^n$.

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% First you have to complete the statement of the lemma.
	% This means that you have to replace both $\phi(a_n,b_n)$ and $\psi(a_n,b_n)$ with explicit formulae.
	% There is no need to show how you worked out what should replace $\phi$ and $\psi$, just enter the replacements into the statement of the lemma and then give the proof as if you always had always known what $\phi$ and $\psi$ are.
	% THE SYMBOLS $\phi$ AND $\psi$ SHOULD NOT APPEAR ANYWHERE IN THE STATEMENT OF THE LEMMA OR THE PROOF WHEN YOU SUBMIT.
	%
	% The proof is by induction.
	%
	First, we want to show that the sequence satisfies the first equation,
	$$\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2}.$$
	When $n=1$ the equations holds,
	\begin{align*}
		\mbox{LHS} = \left(1+\sqrt{2}\right)^1=1+\sqrt{2}\\	
		\mbox{RHS} = a_1+b_1\sqrt{2}=1+\sqrt{2}.
	\end{align*}
	So, $\mbox{LHS} = \mbox{RHS},$ and the equation holds for $n=1$.
	Assume the equations holds for a particular natural number $n$.
	Now, we want to show that the equation also holds for $n+1$.
	From our assumption we know,
	\begin{align*}
		\left(1+\sqrt{2}\right)^n &= a_n + b_n \sqrt{2}\\
		\left(1+\sqrt{2}\right)^n(1+\sqrt{2}) &= (a_n + b_n \sqrt{2})(1+\sqrt{2})\\
		\left(1+\sqrt{2}\right)^{n+1}&= a_n + a_n\sqrt{2} + b_n\sqrt{2} +2b_n\\
		\left(1+\sqrt{2}\right)^{n+1}&= (a_n+2b_n) + (a_n+b_n)\sqrt{2}\\
		\left(1+\sqrt{2}\right)^{n+1} &= (a_{n+1}) + (b_{n+1})\sqrt{2}.
	\end{align*}
	Hence, the equation holds for $n+1$ when it holds for $n$. 
	By induction on $n$, the equation holds for all natural number $n$.

@@

	If $x+1$ is divisible by $n$, then $\frac{x+1}{n}\in \NNzero$ and $0\leq\frac{x+1}{n}\leq x$. Since we know that $P(k)$ is true, we know that there exists an $n$-ary sequence such that 
	$$
		\frac{x+1}{n} = \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^j
	$$
	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $(a_{\frac{x+1}{n}})_{j\in\NN^0}.$
	Manipulating this equation yields, 
	\begin{align*}
		x+1 &= \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^{j+1} \\
		x+1 &= \sum_{j=1}^\infty a_{\frac{x+1}{n},j-1} n^{j}.
	\end{align*}
	Now, let us define a new sequence $(a_{x+1,j})_{j\in\NN^0}$ such that $a_{x+1,j} = a_{\frac{x+1}{n},j-1}$ for all $j\in \NN$ and $a_{x+1,0} = 0 $. We can then rewrite the previous equation as
	\begin{align*}
		x+1 &= 0+ \sum_{j=1}^\infty a_{x+1,j} n^{j} \\
		x+1 &=  \sum_{j=0}^\infty a_{x+1,j} n^{j}.
	\end{align*}
	This new sequence is eventually zero because the original sequence $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ is eventually zero. 
	This new sequence is also $n$-ary because $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ is $n$-ary and we only added another $0$. So we have shown that $P(x+1)$ is true if $x+1$ is divisible by $n$.

	Next, consider the case where $x+1$ is not divisible by $n$. 
	Then, the quotient remainder theorem states that there exists an integer $r$, $1\leq r\leq n-1$ such that $\frac{x+1-r}{n} \in \NN$. 
	So, we can write $0\leq\frac{x+1-r}{n}\leq x$. By our inductive hypothesis, we know
	\begin{align*}
		\frac{x+1-r}{n} &= \sum_{j=0}^\infty a_{\frac{x+1-r}{n},j} n^{j} \\
		x+1-r &= \sum_{j=0}^\infty a_{\frac{x+1-r}{n},j} n^{j+1} \\
		x+1 &= r + \sum_{j=1}^\infty a_{\frac{x+1-r}{n},j-1} n^{j}.
	\end{align*}
	Now, we can define a new sequence $(a_{x+1,j})_{j\in\NN^0}$ such that $a_{x+1,j} = a_{\frac{x+1-r}{n},j-1}$ for all $j\in \NN$ and $a_{x+1,0} = r $. We can then rewrite the previous equation as
	\begin{align*}
		x+1 &= r + \sum_{j=1}^\infty a_{x+1,j} n^{j}\\
		x+1 &= \sum_{j=0}^\infty a_{x+1,j} n^{j}.
	\end{align*}
	This new sequence is eventually zero because the original sequence  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ is eventually zero. This new sequence is also $n$-ary because  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ is $n$-ary, and we added an additional term $r$ which is $1\leq r\leq n-1$. So we have shown that $P(x+1)$ is also true if $x+1$ is not divisible by $n$.

	Therefore $P(x+1)$ is true for all $n\geq2$ for both cases when $x+1$ is and is not divisible by $n$. By complete induction on $x$, $P(x)$ is true, and the theorem is proved.
